Comparison of MCMC algorithms in Stochastic Volatility Models

### 2023-09-28 manuscript/main.tex
updated plots
typo 5k not 1k

@@

@@

>>>>

    \begin{figure}[H]
        \centering
        \includegraphics[scale=0.1]{results/hmc_states_1k.png}
        \caption{Distribution of 1000 rank statistics for centered and non centered Hamiltoninan Monte Carlo (state parameters).}
    \end{figure}

@@

    \begin{figure}[H]
        \centering
        \includegraphics[scale=0.1]{results/hmc_states_5k.png}
        \caption{Distribution of 5000 rank statistics for centered and non centered Hamiltoninan Monte Carlo (state parameters).}
    \end{figure}

@@

    \begin{figure}[H]
        \centering
        \includegraphics[scale=0.1]{results/ksc_5k.png}
        \caption{Distribution of 5000 rank statistics for centered and non centered Gaussian mixture model(static parameters). All parameters display a lack of calibration}
    \end{figure}
